Projecting genetic associations through gene expression patterns highlights disease etiology and drug mechanisms

### 2023-06-28 output/latex/manuscript.tex
update author contributions in latex from previous changes
update author contributions statement

M. Pividori and C.S. Greene conceived and designed the study.
M. Pividori designed the computational methods, performed the experiments, analyzed the data, interpreted the results, and drafted the manuscript.
C.S. Greene supervised the entire project and provided critical guidance throughout the study.
S. Lu and C. Su performed the CRISPR screen with the supervision of S.F.A. Grant.
All authors revised the manuscript and provided critical feedback.

>>>>

M. Pividori and C.S. Greene conceived and designed the study.
M. Pividori designed the computational methods, performed the experiments, analyzed the data, interpreted the results, and drafted the manuscript.
C.S. Greene supervised the entire project and provided critical guidance throughout the study.
S. Lu, C. Su, and M.E. Johnson performed the CRISPR screen with the supervision of S.F.A. Grant.
B. Li provided the TWAS results for eMERGE for replication, and this analysis was supervised by M.D.~Ritchie.
W. Wei, Q. Feng, B. Namjou, K. Kiryluk, I. Kullo, Y. Luo, and M.D.~Ritchie, as part of the eMERGE consortium, provided critical feedback regarding the analyses of this data.
All authors revised the manuscript and provided critical feedback.
